---
title: "Movies' Budgets and Revenues"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(dplyr)
library(tidyr)
library(forcats)
library(ggplot2)

```

```{r parameters, include=FALSE}

min_budget <- 15000
min_revenue <- 0

budget_colour <- "firebrick"
revenue_colour <- "royalblue1"
roi_colour <- "seagreen4"

```

```{r dataextract, include=FALSE}

t <- read_csv('the-movies-dataset/movies_metadata.csv') %>%
  mutate(year = as.integer(format(release_date,'%Y'))) 

summary <- t %>%
  filter(status == "Released") %>%
  mutate(ROI = revenue / budget) %>%
  select(original_title, budget, revenue, ROI) %>%
  filter(budget > min_budget) %>%
  filter(revenue > min_revenue) %>%
  mutate(budget_rank = row_number(budget)) %>% 
  mutate(revenue_rank = row_number(revenue)) 

genremappings <- read_csv("genremappings.csv")

```

An extract of a little over forty-five thousand films was recently used to analyse the budget and American box office revenues of movies.  The data was sourced from [The Movie Database](https://www.themoviedb.org), a community-built database of movies and TV shows. 

# Films with the highest budget and revenue
It seems like every week there are breathless announcements in the entertainment news, that the latest blockbuster has broken some kind of record.  Which films had the highest budgets?

```{r high_budget_movies_cash_sbs, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

summary %>%
  top_n(10, budget_rank) %>%
  mutate(alpha_highlight = ifelse(original_title %in% c('Pirates of the Caribbean: On Stranger Tides','The Lone Ranger'), TRUE, FALSE)) %>%
  mutate(original_title = fct_reorder(original_title, budget)) %>%
  gather(key = field, value = value, budget:revenue) %>%
  mutate(value_mil = value / 10^6) %>%
  mutate(field = case_when(field=="budget"~"Budget",
                           field=="revenue"~"Revenue",
                           TRUE~"Err")) %>%
  mutate(label = ifelse(original_title %in% c('Pirates of the Caribbean: On Stranger Tides','The Lone Ranger'),paste0(field, ": $", round(value_mil,0), " million"), NA)) %>%
  mutate(field = factor(field, ordered = TRUE, levels = c("Revenue", "Budget"))) %>%
  ggplot(aes(x = original_title, y = value_mil, fill = field, alpha = alpha_highlight)) +
  geom_col(position="dodge") +
  geom_text(aes(y = value_mil + 100, label = label), 
            position = position_dodge(width = 1),
            hjust = 0) +
  scale_y_continuous(labels = scales::dollar) +
  scale_alpha_manual(values = c(0.5,1)) +
  scale_fill_manual(values = c(revenue_colour,budget_colour)) +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "top") +
  labs(title = "Pirates: On Stranger Tides cost the most,\nThe Lone Ranger gave the least return",
       x = "",
       y = "$ (millions)",
       fill = "") +
  guides(fill = guide_legend(reverse = TRUE), alpha = FALSE) +
  expand_limits(y = c(0, 3000)) +
  guides(fill=FALSE) +
  NULL

```

The highest budget film in the dataset is _Pirates of the Caribbean: On Stranger Tides_, which cost \$380 million to make.  It did pay off, though; the film had a revenue of \$1 billion from the box office.  On the other hand,  _The Lone Ranger_ earned a paltry \$89 million revenue from its \$255 million dollar budget.  

Therefore, high budgets don't always translate to large amounts of money coming in.  Which films had the highest revenues?

```{r high_revenue_movies_cash_sbs, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

summary %>% 
  top_n(10, revenue_rank) %>%
  mutate(alpha_highlight = ifelse(original_title %in% c("Avatar"),TRUE,FALSE)) %>%
  mutate(original_title = fct_reorder(original_title, revenue)) %>%
  gather(key = field, value = value, budget:revenue) %>%
  mutate(value_mil = value / 10 ^ 6) %>%
  mutate(field = case_when(field=="budget"~"Budget",
                           field=="revenue"~"Revenue",
                           TRUE~"Err")) %>%
  mutate(label = ifelse(original_title %in% c("Avatar"),paste0(field, ": $", round(value_mil,0), " million"), NA)) %>%
  mutate(field = factor(field, ordered = TRUE, levels = c("Revenue", "Budget"))) %>%
  ggplot(aes(x = original_title, y = value_mil, fill = field, alpha = alpha_highlight)) +
  geom_col(position = "dodge") +
  geom_text(aes(y = 1000, label = label, col = field), 
            position = position_dodge(width = 1),
            hjust = 0) +
  scale_y_continuous(labels = scales::dollar) +
  scale_alpha_manual(values = c(0.5,1)) +
  scale_fill_manual(values = c(revenue_colour, budget_colour)) +
  scale_color_manual(values = c("Budget" = "black", "Revenue" = "white")) +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "top") +
  labs(title = "Avatar had the highest US box office revenue",
       x = "",
       y = "$ (millions)",
       fill = "") +
  guides(fill = guide_legend(reverse = TRUE), alpha = FALSE) +
  expand_limits(y = c(0, 3000)) +
  guides(fill=FALSE, col=FALSE) +
  NULL

```

The highest revenue film was _Avatar_, which made \$2.8 billion.  Interestingly, there is little-to-no crossover between the two charts; high budgets don't always translate to high revenues.

# Return on Investment (ROI)
So, if high budgets don't give high revenues, what does?  Here are the films with the highest return on investment (`revenue / budget`) in the dataset.

```{r high_ROIs, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

summary %>%
  top_n(20, ROI) %>%
  mutate(alpha_highlight = ifelse(original_title %in% c("The Blair Witch Project"), TRUE, FALSE)) %>%
  mutate(original_title = fct_reorder(original_title, ROI)) %>%
  mutate(label = ifelse(original_title %in% c("The Blair Witch Project"), paste0("ROI: ", round(ROI,1)),NA)) %>%
  ggplot(aes(x = original_title, y = ROI, alpha = alpha_highlight)) +
  geom_col(fill = roi_colour) +
  geom_text(aes(y = 2000, label = label), col = "white") +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "none") +
  scale_alpha_manual(values = c(0.5, 1)) +
  labs(title = "The Blair Witch Project had an extremely high ROI",
       x = "",
       y = "ROI") +
  guides(alpha = FALSE) +
  NULL


```

Obviously, the major outlier here is _The Blair Witch Project_, which made \$250 million off its budget of \$60 thousand.  It's worth noting that a number of other films in this list are also  horror movies; it seems they're cheap to make and sometimes become cult classics.  The film with the Chinese title in second place is [The Way of the Dragon](https://www.imdb.com/title/tt0068935/), a 1972 martial arts flick starring Bruce Lee.

Aside from the horror films already mentioned, there are also a handful of early Disney animated movies on the list; Disney was well known for under-paying its staff in the early days, to the point where [the animators went on strike in 1941](https://en.wikipedia.org/wiki/Disney_animators%27_strike); this may well have contributed to the low budgetary costs of the films in question.

# Conclusion
In general, the films that make the most revenue are the ones with a significant budget, but generally not the *most* investment.  Yet outliers such as _The Blair Witch Project_ buck the trend and demonstrate that even lower-budget films can be smash hits in the right circumstances, while _The Lone Ranger_ shows that higher-budget films can still flop.

# Further reading
This was an edited excerpt from a more general exploration of this dataset.  If you wish to read the full analysis, it is available [here](http://rpubs.com/mm-c/movies).

<br>